Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2021-05-17 main.tex
Biography update
Started with huge overhaul New section structure created Correct labels added for sections Simply removed references to previous section (means many paragraphs now read wrong) Copied relevant parts of paper into their new sections (still need lots of work to make them read fluid) Removed sections will no longer be included (but references to them are still present - need to be removed)

\section{Introduction}
\IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}. Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localization methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004}, and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}. Range-based localization methods, including the use of radar measurements, GPS clocks, and signal strength measurements, have found particularly large applications due to their robustness and accuracy. These methods use distance measurements to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location, and observations centrally. Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicious gain. With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made the requirements of information security and user privacy more apparent than before \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}. For example, an aircraft localization scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles. Or in autonomous vehicle state estimation, benefit from neighboring vehicles' information may be desired while no participant wishes to share information about their hardware. Additionally, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations. All of these scenarios, and the one we will consider, require methods for computing specific operations while ensuring the privacy of some or all of the input data. Our contributions in this work will be presented in two parts. We first propose a novel aggregation-based encryption scheme which allows the private aggregation of weighted sums, before developing a computationally plausible localization filter in the presence of range-only sensors using this scheme, such that sensor and navigator privacy is preserved.

The remainder of the paper is structured as follows. In Section \ref{sec:lit_overview} we give an overview of the relevant literature to the topic and in Section \ref{sec:problem_statement} we introduce the localization problem, the relevant aggregation operation for its solution and the restrictions on involved parties. Sections \ref{sec:crypto_prelim} and \ref{sec:lcao_definition} will summarize cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it. Sections \ref{sec:loc_prelim} and \ref{sec:priv_localization} introduce localization preliminaries and our privacy-preserving localization method using the private aggregation scheme. We show and discuss simulation results in Section \ref{sec:sim_and_results} and conclude our work in Section \ref{sec:conclusion}.

% 
% 888      8888888 88888888888 
% 888        888       888     
% 888        888       888     
% 888        888       888     
% 888        888       888     
% 888        888       888     
% 888        888       888     
% 88888888 8888888     888     
%                              
%                              
%                              
%

\section{Literature Overview} \label{sec:lit_overview}
In this section, we will discuss methods for providing security guarantees in signal processing tasks, and their applications to localization and estimation problems.

% 
% ######## ##    ##  ######      ######   ######  ##     ## ######## ##     ## ########  ######  
% ##       ###   ## ##    ##    ##    ## ##    ## ##     ## ##       ###   ### ##       ##    ## 
% ##       ####  ## ##          ##       ##       ##     ## ##       #### #### ##       ##       
% ######   ## ## ## ##           ######  ##       ######### ######   ## ### ## ######    ######  
% ##       ##  #### ##                ## ##       ##     ## ##       ##     ## ##             ## 
% ##       ##   ### ##    ##    ##    ## ##    ## ##     ## ##       ##     ## ##       ##    ## 
% ######## ##    ##  ######      ######   ######  ##     ## ######## ##     ## ########  ######  
%

\subsection{Encryption Schemes in Signal Processing}

@@

% 
% ######## ##    ##  ######     ##        #######   ######  
% ##       ###   ## ##    ##    ##       ##     ## ##    ## 
% ##       ####  ## ##          ##       ##     ## ##       
% ######   ## ## ## ##          ##       ##     ## ##       
% ##       ##  #### ##          ##       ##     ## ##       
% ##       ##   ### ##    ##    ##       ##     ## ##    ## 
% ######## ##    ##  ######     ########  #######   ######  
%

\subsection{Applications to Localization and Estimation}
Localization methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors. We aim to provide an accurate localization filter in the presence of range-only sensors while providing uncertainties associated with estimates.

@@

Encrypted model-predictive-control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation. In \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, the novel security notions of private weighted sum aggregation with centralized or hidden weights (pWSAc and pWSAh, respectively) are proposed. The schemes capture a weighted aggregation operation suitable for providing privacy in some control environments and are similar in principle to the aggregation decomposition proposed in this work. The requirements of our aggregation operation differ, however, in that weights are generalized to arbitrary length linear-combinations, which must be consistent across all participants, and can vary over time. We also require a formal security proof capturing these weight requirements as well as the explicit capabilities of participants. We define our alternative security notion in Section \ref{sec:lcao_definition}.

Along with encryption schemes and their application to localization-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers. As is the case with range sensors, real-valued measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations. Google's Encrypted BigQuery Client \cite{googleEncryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme. It, however, leaks the exponent information of encrypted numbers. In \cite{farokhiSecurePrivateControl2017}, a simpler alternative is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings. We use a modified version of \cite{farokhiSecurePrivateControl2017} due to its simplicity and applicability, and introduce the scheme details in Section \ref{sec:loc_prelim}.

@@

\section{Problem Statement} \label{sec:problem_statement}
The localization scenario we consider in this work is that of Bayesian self-navigation using range-only sensors. We consider localization in the two-dimensional case for simplicity but will derive methods suitable for an extension to the three-dimensional equivalent.

% 
% ########  ########  ######   #######  ##     ## ########  
% ##     ## ##       ##    ## ##     ## ###   ### ##     ## 
% ##     ## ##       ##       ##     ## #### #### ##     ## 
% ##     ## ######   ##       ##     ## ## ### ## ########  
% ##     ## ##       ##       ##     ## ##     ## ##        
% ##     ## ##       ##    ## ##     ## ##     ## ##        
% ########  ########  ######   #######  ##     ## ##        
%

\subsection{Problem Decomposition} \label{subsec:problem_decomposition}
The recursive nature of the problem definition above complicates the defining and proving of security requirements for the localization scenario. As with existing estimation methods \cite{benhamoudaNewFrameworkPrivacyPreserving2016,alexandruEncryptedCooperativeControl2019} we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable.

@@

In Section \ref{sec:priv_localization}, we will show how this protocol is sufficient to compute the required estimation information at the sensors needed to update the navigator's estimation filter.

\begin{remark}
    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ by the navigator, requiring only uni-directional communication by sending values $a_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section \ref{subsec:algorithm}.
\end{remark}

% 
%  ######     ###    ########     ###    ########  #### ##       #### ######## #### ########  ######  
% ##    ##   ## ##   ##     ##   ## ##   ##     ##  ##  ##        ##     ##     ##  ##       ##    ## 
% ##        ##   ##  ##     ##  ##   ##  ##     ##  ##  ##        ##     ##     ##  ##       ##       
% ##       ##     ## ########  ##     ## ########   ##  ##        ##     ##     ##  ######    ######  
% ##       ######### ##        ######### ##     ##  ##  ##        ##     ##     ##  ##             ## 
% ##    ## ##     ## ##        ##     ## ##     ##  ##  ##        ##     ##     ##  ##       ##    ## 
%  ######  ##     ## ##        ##     ## ########  #### ######## ####    ##    #### ########  ######  
%

\subsection{Participant Capabilities} \label{subsec:capabilities}
Before we can define formal security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
\begin{LaTeXdescription}
    \item[Global Navigator Broadcast] From the decomposition defined above, we know that bi-directional communication between navigator and sensors is required. We make the assumption that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.

@@

\subsection{Inherent Leakage}
Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, however, we stress that in any estimation problem where process and measurement models are known, knowledge of sequential state estimates as is the case at the navigator, or the knowledge of one or more measurements as is the case by one or more malicious sensors, naturally leads to the leakage of some information. For this reason, we accept that average sensor information may be leaked to the navigator and that less accurate estimates of location may be leaked to sensors. We will instead show that individual sensor information remains private to sensors and that the most precise localization estimate, requiring all measurements, remains private to the navigator.

% 
% 8888888888 888b    888  .d8888b.       8888888b.  8888888b.  8888888888 888      8888888 888b     d888 
% 888        8888b   888 d88P  Y88b      888   Y88b 888   Y88b 888        888        888   8888b   d8888 
% 888        88888b  888 888    888      888    888 888    888 888        888        888   88888b.d88888 
% 8888888    888Y88b 888 888             888   d88P 888   d88P 8888888    888        888   888Y88888P888 
% 888        888 Y88b888 888             8888888P"  8888888P"  888        888        888   888 Y888P 888 
% 888        888  Y88888 888    888      888        888 T88b   888        888        888   888  Y8P  888 
% 888        888   Y8888 Y88b  d88P      888        888  T88b  888        888        888   888   "   888 
% 8888888888 888    Y888  "Y8888P"       888        888   T88b 8888888888 88888888 8888888 888       888 
%                                                                                                        
%                                                                                                        
%                                                                                                        
%

\section{Cryptography Preliminaries} \label{sec:crypto_prelim}
When defining our aggregation security requirements and encryption scheme we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.

% 
%  ######  ########  ######  ##     ## ########  #### ######## ##    ## 
% ##    ## ##       ##    ## ##     ## ##     ##  ##     ##     ##  ##  
% ##       ##       ##       ##     ## ##     ##  ##     ##      ####   
%  ######  ######   ##       ##     ## ########   ##     ##       ##    
%       ## ##       ##       ##     ## ##   ##    ##     ##       ##    
% ##    ## ##       ##    ## ##     ## ##    ##   ##     ##       ##    
%  ######  ########  ######   #######  ##     ## ####    ##       ##    
%

\subsection{Security Notions}
The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}. The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}, while for private aggregation schemes, the notion is Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. 
\begin{definition}
An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption. The formal security game and definition for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
\end{definition}
\begin{definition}
An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum. The formal security game and definition for AO has been given in Appendix \ref{app:ao}.
\end{definition}

@@

% 
% 8888888888 888b    888  .d8888b.       8888888b.  8888888b.   .d88888b.  888888b.   
% 888        8888b   888 d88P  Y88b      888   Y88b 888   Y88b d88P" "Y88b 888  "88b  
% 888        88888b  888 888    888      888    888 888    888 888     888 888  .88P  
% 8888888    888Y88b 888 888             888   d88P 888   d88P 888     888 8888888K.  
% 888        888 Y88b888 888             8888888P"  8888888P"  888     888 888  "Y88b 
% 888        888  Y88888 888    888      888        888 T88b   888     888 888    888 
% 888        888   Y8888 Y88b  d88P      888        888  T88b  Y88b. .d88P 888   d88P 
% 8888888888 888    Y888  "Y8888P"       888        888   T88b  "Y88888P"  8888888P"  
%                                                                                     
%                                                                                     
%                                                                                     
%

\section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
As stated in Section \ref{subsec:problem_decomposition}, we decompose the localization method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors. To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation. Broadly speaking, we want a cryptographic scheme which allows instances of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme. That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations. This can be summarized by the two informal security notions:
\begin{LaTeXdescription}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances. Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
\end{LaTeXdescription}

% 
% ##        ######     ###     #######  
% ##       ##    ##   ## ##   ##     ## 
% ##       ##        ##   ##  ##     ## 
% ##       ##       ##     ## ##     ## 
% ##       ##       ######### ##     ## 
% ##       ##    ## ##     ## ##     ## 
% ########  ######  ##     ##  #######  
%

\subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. These are used by a trusted third party, an aggregator, and value producing users $i,\,1\leq i \leq n$. They are defined as follows

We formalize the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger:

\begin{LaTeXdescription}
    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{LaTeXenumerate}
        \item \textit{Encryption:} The attacker chooses a value $x$ and computes an encryption of $x$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(x)$.
        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ and $(i',t',a^{\prime(t')}_{i',1},\dots,a^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies a^{(t)}_{i,j} = a^{\prime(t')}_{i',j},\,1\leq j\leq m\,.
        \end{equation*}
        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{LaTeXenumerate} 
    \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
    \end{equation*}
    and
    \begin{equation*}
        \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.}, the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \left\langle\mathcal{E}_{pk_0,sk_i}\left(\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i\in S\right\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{LaTeXdescription}

% 
%  #######  ##     ## ########      ######   ######  ##     ## ######## ##     ## ######## 
% ##     ## ##     ## ##     ##    ##    ## ##    ## ##     ## ##       ###   ### ##       
% ##     ## ##     ## ##     ##    ##       ##       ##     ## ##       #### #### ##       
% ##     ## ##     ## ########      ######  ##       ######### ######   ## ### ## ######   
% ##     ## ##     ## ##   ##            ## ##       ##     ## ##       ##     ## ##       
% ##     ## ##     ## ##    ##     ##    ## ##    ## ##     ## ##       ##     ## ##       
%  #######   #######  ##     ##     ######   ######  ##     ## ######## ##     ## ######## 
%

\subsection{Our Scheme Meeting LCAO Security} \label{subsec:our_scheme}
Our scheme is based on the Paillier and Joye-Libert schemes introduced in Sections \ref{subsec:paillier_scheme} and \ref{subsec:joye_libert_scheme}, and similarly bases its security on the DCRA. As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys. Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.

@@

    \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
    \State $\rvec{x}_{k|k-1} \gets \vec{f}(\rvec{x}_{k-1|k-1})$
    \State $\mat{P}_{k|k-1} \gets \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}$

>>>>

\section{Introduction} \label{sec:introduction}
\IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}. Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localization methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004}, and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}. Range-based localization methods, including the use of radar measurements, GPS clocks, and signal strength measurements, have found particularly large applications due to their robustness and accuracy. These methods use distance measurements to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location, and observations centrally. Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicious gain. With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made the requirements of information security and user privacy more apparent than before \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}. For example, an aircraft localization scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles. Or in autonomous vehicle state estimation, benefit from neighboring vehicles' information may be desired while no participant wishes to share information about their hardware. Additionally, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations. All of these scenarios, and the one we will consider, require methods for computing specific operations while ensuring the privacy of some or all of the input data. Our contributions in this work will be presented in two parts. We first propose a novel aggregation-based encryption scheme which allows the private aggregation of weighted sums, before developing a computationally plausible localization filter in the presence of range-only sensors using this scheme, such that sensor and navigator privacy is preserved.

The remainder of the paper is structured as follows. In Section  we give an overview of the relevant literature to the topic and in Section  we introduce the localization problem, the relevant aggregation operation for its solution and the restrictions on involved parties. Sections  and  will summarize cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it. Sections  and  introduce localization preliminaries and our privacy-preserving localization method using the private aggregation scheme. We show and discuss simulation results in Section  and conclude our work in Section .

% LITERATURE OVERVIEW

\label{sec:lit_overview}
In this section, we will discuss methods for providing security guarantees in signal processing tasks, and their applications to localization and estimation problems.

% ENCRYPTION SCHEMES IN SIGNAL PROCESSING

@@

% APPLICATIONS TO LOCALIZATION AND ESTIMATION

Localization methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors. We aim to provide an accurate localization filter in the presence of range-only sensors while providing uncertainties associated with estimates.

@@

Encrypted model-predictive-control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation. In \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, the novel security notions of private weighted sum aggregation with centralized or hidden weights (pWSAc and pWSAh, respectively) are proposed. The schemes capture a weighted aggregation operation suitable for providing privacy in some control environments and are similar in principle to the aggregation decomposition proposed in this work. The requirements of our aggregation operation differ, however, in that weights are generalized to arbitrary length linear-combinations, which must be consistent across all participants, and can vary over time. We also require a formal security proof capturing these weight requirements as well as the explicit capabilities of participants. We define our alternative security notion in Section .

Along with encryption schemes and their application to localization-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers. As is the case with range sensors, real-valued measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations. Google's Encrypted BigQuery Client \cite{googleEncryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme. It, however, leaks the exponent information of encrypted numbers. In \cite{farokhiSecurePrivateControl2017}, a simpler alternative is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings. We use a modified version of \cite{farokhiSecurePrivateControl2017} due to its simplicity and applicability, and introduce the scheme details in Section .

@@

\section{Problem Statement} \label{sec:problem_statement}

% DECOMPOSITION

The recursive nature of the problem definition above complicates the defining and proving of security requirements for the localization scenario. As with existing estimation methods \cite{benhamoudaNewFrameworkPrivacyPreserving2016,alexandruEncryptedCooperativeControl2019} we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable.

@@

In Section , we will show how this protocol is sufficient to compute the required estimation information at the sensors needed to update the navigator's estimation filter.

\begin{remark}
    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ by the navigator, requiring only uni-directional communication by sending values $a_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section .
\end{remark}

% 
%  ######  ########  ##    ## ########  ########  #######     ########  ########   #######  ########  
% ##    ## ##     ##  ##  ##  ##     ##    ##    ##     ##    ##     ## ##     ## ##     ## ##     ## 
% ##       ##     ##   ####   ##     ##    ##    ##     ##    ##     ## ##     ## ##     ## ##     ## 
% ##       ########     ##    ########     ##    ##     ##    ########  ########  ##     ## ########  
% ##       ##   ##      ##    ##           ##    ##     ##    ##        ##   ##   ##     ## ##     ## 
% ##    ## ##    ##     ##    ##           ##    ##     ##    ##        ##    ##  ##     ## ##     ## 
%  ######  ##     ##    ##    ##           ##     #######     ##        ##     ##  #######  ########  
%

\subsection{Formal Cryptographic Problem} \label{subsec:crypto_problem}

% CAPABILITIES

Before we can define formal security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
\begin{LaTeXdescription}
    \item[Global Navigator Broadcast] From the decomposition defined above, we know that bi-directional communication between navigator and sensors is required. We make the assumption that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.

@@

% LCAO OVERVIEW

As stated in Section, we decompose the localization method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors. To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation. Broadly speaking, we want a cryptographic scheme which allows instances of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme. That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations. This can be summarized by the two informal security notions:
\begin{LaTeXdescription}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances. Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
\end{LaTeXdescription}

% LINEAR-COMBINATION AGGREGATOR OBLIVIOUS ENCRYPTION

\label{subsec:lcao}
We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. These are used by a trusted third party, an aggregator, and value producing users $i,\,1\leq i \leq n$. They are defined as follows

We formalize the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger: %see appendix

% 
% ########  ######  ########    ########  ########   #######  ########  
% ##       ##    ##    ##       ##     ## ##     ## ##     ## ##     ## 
% ##       ##          ##       ##     ## ##     ## ##     ## ##     ## 
% ######    ######     ##       ########  ########  ##     ## ########  
% ##             ##    ##       ##        ##   ##   ##     ## ##     ## 
% ##       ##    ##    ##       ##        ##    ##  ##     ## ##     ## 
% ########  ######     ##       ##        ##     ##  #######  ########  
%

\subsection{Estimation problem} \label{subsec:est_problem}
The localization scenario we consider in this work is that of Bayesian self-navigation using range-only sensors. We consider localization in the two-dimensional case for simplicity but will derive methods suitable for an extension to the three-dimensional equivalent.

% LEAKAGE

Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, however, we stress that in any estimation problem where process and measurement models are known, knowledge of sequential state estimates as is the case at the navigator, or the knowledge of one or more measurements as is the case by one or more malicious sensors, naturally leads to the leakage of some information. For this reason, we accept that average sensor information may be leaked to the navigator and that less accurate estimates of location may be leaked to sensors. We will instead show that individual sensor information remains private to sensors and that the most precise localization estimate, requiring all measurements, remains private to the navigator.

% 
% 8888888b.  8888888b.  8888888888 888      8888888 888b     d888  .d8888b.  
% 888   Y88b 888   Y88b 888        888        888   8888b   d8888 d88P  Y88b 
% 888    888 888    888 888        888        888   88888b.d88888 Y88b.      
% 888   d88P 888   d88P 8888888    888        888   888Y88888P888  "Y888b.   
% 8888888P"  8888888P"  888        888        888   888 Y888P 888     "Y88b. 
% 888        888 T88b   888        888        888   888  Y8P  888       "888 
% 888        888  T88b  888        888        888   888   "   888 Y88b  d88P 
% 888        888   T88b 8888888888 88888888 8888888 888       888  "Y8888P"  
%                                                                            
%                                                                            
%                                                                            
%

\section{Preliminaries} \label{sec:preliminaries}
When defining our aggregation security requirements and encryption scheme we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.

% SECURITY NOTIONS

The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}. The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}, while for private aggregation schemes, the notion is Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. 
\begin{definition}
An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption. The formal security game and definition for IND-CPA has been given in Appendix .
\end{definition}
\begin{definition}
An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum. The formal security game and definition for AO has been given in Appendix .
\end{definition}

@@

\subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}

% INTRO

Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localization filter. The filter we introduce requires the use of real-valued inputs and functions, and relies on a non-linear measurement model. We will make use of a real-number encoding scheme supporting our required homomorphic operations as well as a reformulated Extended Kalman Filter which reduces the filter update step to use only these operations.

% ENCODING

In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{a \,|\, a \in \mathbb{Z}_N\}$. For this reason, a quantization and integer mapping method for real numbers is required for their encryption and homomorphic processing. We quantize with a generalized Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.

% 
% 888      .d8888b.        d8888  .d88888b.  
% 888     d88P  Y88b      d88888 d88P" "Y88b 
% 888     888    888     d88P888 888     888 
% 888     888           d88P 888 888     888 
% 888     888          d88P  888 888     888 
% 888     888    888  d88P   888 888     888 
% 888     Y88b  d88P d8888888888 Y88b. .d88P 
% 88888888 "Y8888P" d88P     888  "Y88888P"  
%                                            
%                                            
%                                            
%

\section{Private Linear-Combination Aggregation Scheme} \label{sec:lcao_scheme}

% OUR SCHEME MEETING LCAO SECURITY

\label{subsec:our_scheme}
Our scheme is based on the Paillier and Joye-Libert schemes introduced in Sections \ref{subsec:paillier_scheme} and \ref{subsec:joye_libert_scheme}, and similarly bases its security on the DCRA. As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys. Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.

@@

    \State Compute $\mat{F}_k$ by 
    \State $\rvec{x}_{k|k-1} \gets \vec{f}(\rvec{x}_{k-1|k-1})$
    \State $\mat{P}_{k|k-1} \gets \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}$
